### 2019-01-04 papers/journal/experiments.tex
added results for existential case

The minimal connectivity results for each variation of the existential condition is presented in table~\ref{tab:smt-grph}.
%
Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we have fixed the total number of molecules ($|M|$) to be $2|N|$ 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%
In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation F of 2-connected, 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where the instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.

>>>>

The minimal connectivity results for each variation of the existential condition is presented in table~\ref{tab:smt-grph}.
%
No matter what the rules of molecular
interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
%
Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is necessary and sufficient for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For more constrained regulation models
(including the case where SNAREs are always active) we did not find any possible graphs
representing steady state vesicle transport networks. 
%
This strongly suggests (but does not
prove, since we only checked graphs of finite size) that no such graphs exist.
%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
%%
%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
%%  
%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
%%
%Variants C has 3-connectedness as

\todo{SA: Explain the results in details and Add biological interpretation of results.}
%
Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we have fixed the total number of molecules ($|M|$) to be $2|N|$ 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%
In the table ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation F of 2-connected, 10 compartment graph took 129.78 minutes (7786.8 secs) with a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran OUT OF MEMORY.
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where the instance was unsatisfiable (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $20$ nodes.
